The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update 'Ontological Architecture'

  \item ANNOdc (\cref{sec:core}, \cref{fig:core}) is a domain-core (dc) ontology to provide the core entities of a domain, such as, inter alia, 
the general anatomical categories (\enquote{Anatomical structure} and \enquote{Landmark}), categories for describing different characteristics of 
landmarks (\enquote{Landmark location}, \enquote{Landmark property} and \enquote{Landmark line region}) as well as 
the category \enquote{Phenotype} to model the rules for determining human phenotypes. The ANNOdc is founded by \emph{General Formal Ontology} (GFO)~\citep{gfo}.

  \item GFO is a top-level ontology for integrating and founding the ANNO. In the current paper, we refer especially to the categories 
\enquote{Material object}, \enquote{Attributive}, \enquote{Relator} as well as the spatial entities of GFO (\cref{sec:core}, \cref{fig:gfo}).
\end{enumerate}

>>>>

  \item ANNOdc (\cref{sec:core}, \cref{fig:core}) is a domain-core (dc) ontology to provide the core entities of a domain, such as, inter alia, 
the general anatomical categories (\aurl{anno}{Anatomical_structure} and \aurl{anno}{Landmark}), categories for describing different characteristics of 
landmarks (\aurl{anno}{Landmark_location}, \aurl{anno}{Landmark_property} and \aurl{anno}{Landmark_line_region}) as well as 
the category \aurl{anno}{Phenotype} to model the rules for determining human phenotypes. The ANNOdc is founded by \emph{General Formal Ontology} (GFO)~\citep{gfo}.

  \item GFO is a top-level ontology and is used for integrating and founding the ANNO. In the current paper, we refer especially to the categories 
\aurl{gfo}{Material_object}, \aurl{gfo}{Attributive}, \aurl{gfo}{Relator} as well as the spatial entities of GFO, \aurl{gfo}{Line_region} and \aurl{gfo}{Surface_region} (\cref{sec:core}, \cref{fig:gfo}).
\end{enumerate}
